---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Homework 8: Building your own R package

## Package Installation
We will use the `devtools` package to facilitate package development. `Devtools` and my package can be installed with the following commands, and both could be loaded with `library` command.

```{r, tidy=TRUE}
library(devtools)
```

```{r, tidy=TRUE}
#load_all()
devtools::install_github("zhengdong91/hw8")
library(hw8)
library(gapminder)
```

## Function Testing


## Conclusion

There are four functions in the package, we designed `Quantiles` and `Top20GdpPercap` functions to deal with the gapminder dataset, `Quantiles` return the difference of a numeric variable, and `Top20GdpPercap` return the top 20 GdpPercap countries in a particular year. I also inplemented two functions `fbind` and `freq_out` Jenny shared with us in the classes as a practice. 


#### Some useful links:
+ [Write your own R package, Part One](https://stat545-ubc.github.io/packages04_foofactors-package-01.html)
+ [Write your own R package, Part Two](https://stat545-ubc.github.io/packages05_foofactors-package-02.html)
