---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Homework 8: Building your own R package

## Package Installation
We will use the `devtools` package to facilitate package development. `Devtools` and my package can be installed with the following commands, and both could be loaded with `library` command.

```{r, tidy=TRUE}
library(devtools)
```

```{r, tidy=TRUE}
load_all()
# devtools::install_github("zhengdong91/hw8")
library(hw8)
library(gapminder)
```

## Function Testing

There are four functions in the package, we designed `Quantiles` and `Top20GdpPercap` functions to deal with the gapminder dataset, `Quantiles` return the difference of a numeric variable, and `Top20GdpPercap` return the top 20 GdpPercap countries in a particular year. I also inplemented two functions `fbind` and `freq_out` Jenny shared with us in the classes as a practice. 

```{r, tidy=TRUE}
Top20GdpPercap(2002)
```


```{r, tidy=TRUE}
qdiff1(gapminder$lifeExp, probs = c(0.25, 0.75))
qdiff1(gapminder$lifeExp, probs = c(0, 1))
```

```{r, tidy=TRUE}
a <- factor(c("character", "hits", "your", "eyeballs"))
b <- factor(c("but", "integer", "where it", "counts"))
fbind(a, b)
```

```{r, tidy=TRUE}
freq_out(iris$Species)
```

#### Some useful links:

  + [data-raw](https://github.com/jennybc/candy/tree/master/data-raw)
  + [explore and clean dataset](https://github.com/jennybc/candy/blob/master/data-raw/00_explore-raw.R)
  + [An introduction to data cleaning with R](https://cran.r-project.org/doc/contrib/de_Jonge+van_der_Loo-Introduction_to_data_cleaning_with_R.pdf)
