---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
# Homework 8: Building your own R package

## Package Installation
We will use the `devtools` package to facilitate package development. `Devtools` and my package can be installed with the following commands, and both could be loaded with `library` command.

```{r, tidy=TRUE}
library(devtools)
```

```{r, tidy=TRUE}
devtools::install_github("zhengdong91/hw8")
library(hw8)
```

## Function Testing

There are four functions in the package, we designed `Quantiles` and `Top20GdpPercap` functions to deal with the gapminder dataset, `Quantiles` return the difference of a numeric variable, and `Top20GdpPercap` return the top 20 GdpPercap countries in a particular year. I also inplemented two functions `fbind` and `freq_out` Jenny shared with us in the classes as a practice. 

```{r, tidy=TRUE}
Top20GdpPercap(2002)
```

```{r, tidy=TRUE}
qdiff1(gapminder$lifeExp)
```

```{r, tidy=TRUE}
a <- factor(c("character", "hits", "your", "eyeballs"))
b <- factor(c("but", "integer", "where it", "counts"))
fbind(a, b)
```

```{r, tidy=TRUE}
freq_out(iris$Species)
```